---
title: 'Data Wrangling: Homework 12'
author: "Alex Poplawski"
date: "4/22/2026"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r}
library(readxl)
library(writexl)
library(janitor)
library(dplyr)
library(ggplot2)
library(knitr)
library(duckdb)
library(DBI)
```

## Penguin Excel Spreadsheet

### Three Worksheets Loaded
```{r}
torgersen_penguins <- read_excel("penguins.xlsx",
sheet = "Torgersen Island", na = "NA") %>%
  clean_names()

biscoe_penguins <- read_excel("penguins.xlsx",
sheet = "Biscoe Island", na = "NA") %>%
  clean_names()

dream_penguins <- read_excel("penguins.xlsx",
sheet = "Dream Island", na = "NA") %>%
  clean_names

torgersen_penguins
biscoe_penguins
dream_penguins
```
^[Question 1 Complete.]

### Stacked Dataset
```{r}
stacked_data <- bind_rows(
  torgersen_penguins, biscoe_penguins, dream_penguins
)
stacked_data
```
^[Question 2 Complete.]

### Faceted Scatterplot of Bill Depth Versus Bill Length
```{r}
ggplot(stacked_data, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point() +
  facet_wrap(~island)
```
^[Question 3 Complete.]

### Average Body masses of the Different Penguin Species.
```{r}
species_average_body_mass <- stacked_data %>%
  group_by(species) %>%
  summarize(average_mass = round(mean(body_mass_g, na.rm = TRUE), 2))

species_average_body_mass %>%
  kable()
```
^[Question 4 Complete.]

--------------------------------------------------------------------------------------------------------------------------------

## Penguin Database

### DuckDB Database
```{r}
con <- DBI::dbConnect(duckdb::duckdb())
con
```
^[Question 1 Complete.]

### Combined Penguins Tibble to Database
```{r}
dbWriteTable(con, "penguins", stacked_data, overwrite = TRUE)
dbListTables(con)
```
^[Question 2 Complete.]
